---
title: "Instance results"
output:
  html_document:
    self_contained: yes
    theme: united
    highlight: tango
    # df_print: paged
    # code_folding: show
    toc: true
    toc_float: true
    number_sections: true
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, encoding) { 
    out_dir <- here::here("docs/");
    rmarkdown::render(inputFile,
                      encoding=encoding, 
                      output_file=file.path(out_dir, 'results.html')) })
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
here::i_am("results/results.Rmd")  # specify relative path given project
# remotes::install_github("relund/gMOIP")
# remotes::install_github("fischuu/OjaNP")
# library(gMOIP)
library(DT)
library(tidyverse)
# library(knitr)
# library(rgl)
# rgl::setupKnitr()
# options(rgl.useNULL=TRUE)
# rgl::par3d("family" = "serif")
conflicted::conflicts_prefer(plotly::layout)
conflicted::conflicts_prefer(dplyr::filter)
knitr::opts_chunk$set(
  echo = FALSE,
  message=FALSE, include = TRUE, warning = FALSE,
  out.width = "99%", fig.width = 12, fig.align = "center", fig.asp = 0.8
)
```

This report contains different preliminary plots and tables that may be relevant for analyzing the results. Given a problem consisting of $m$ subproblems with $Y_N^s$ given for each subproblem $s$, we use a filtering algorithm to find $Y_N$. 

The following instance/problem groups are generated given:

  * $p=2,\ldots, 5$. 
  * $S=2,\ldots 5$ where $S$ is the number of subproblems. 
  * All subproblems have the same method config or half have method `u` and `l`.
  * Five instances for each config. 

```{r}
datFull <- read_csv(here::here("results/results.csv"))
```


`r nrow(datFull)` problems have been solved.

```{r}
# remove results where have not solved all instances
dat <- datFull |> 
  group_by(p, m, method, spCard1) %>% 
  filter(n() == 5) %>% 
  ungroup() |> view()
```

## Size of $Y_N$

What is $|Y_N|$ given the different methods of generating the set of nondominated points for the subproblems?

```{r}
dat %>% 
  group_by(method) %>% 
  summarise(mean_card = mean(card), n = n()) 
```

We use plots to check for effects of $p$, $m$ and subset size:

```{r}
dat %>% 
  ggplot(aes(x = spAveCard, y = card, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ m, scales = "free", labeller =  "label_both")  + 
  labs(title = "Number of nondominated points given subproblem cardinality",
       y = "Cardinality Yn",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = spAveCard, y = card, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_wrap(p ~ m, scales = "free", labeller =  "label_both")  + 
  labs(title = "Number of nondominated points given subproblem cardinality",
       y = "Cardinality Yn",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = spAveCard, y = card, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ m, scales = "free_y", labeller = "label_both")  + 
  labs(title = "Number of nondominated points given subproblem cardinality (log2) scale",
       y = "Cardinality Yn",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") +
  scale_y_continuous(trans = "log2")
```


```{r}
dat %>% 
  ggplot(aes(x = p, y = card, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(m ~ spAveCard, scales = "free_y", labeller =  "label_both")  + 
  labs(title = "Number of nondominated points given subproblem cardinality",
       y = "Cardinality Yn",
       x = "p",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = m, y = card, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ spAveCard, scales = "free_y", labeller =  "label_both")  + 
  labs(title = "Number of nondominated points given subproblem cardinality",
       y = "Cardinality Yn",
       x = "m",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>%
  ggplot(aes(x = spAveCard, y = card, color = factor(p))) +
  geom_point() +
  stat_summary(fun="mean", geom="line") +
  facet_wrap(vars(method), scales = "free", labeller = "label_both")  +
  labs(title = "Number of nondominated points given subproblem cardinality",
       y = "Cardinality Yn",
       x = "Subproblem cardinality",
       color = "p") +
  theme(legend.position = "bottom")
```

```{r}
dat %>% 
  ggplot(aes(x = spAvePctExt, y = card, color = factor(spAveCard), shape = method, group = method)) +
    stat_summary(fun="mean", geom="line", color = "gray70") +
    # stat_summary(aes(group = factor(spAveCard), color = factor(spAveCard)), fun="mean", geom="line", size = 0.05) +
    geom_point() + 
    facet_grid(p ~ m, scales = "free_y", labeller =  "label_both")  + 
    labs(title = "Number of nondominated points",
       y = "Cardinality Yn",
       x = "Ave relative number of subproblem extreme",
       color = "Subproblem cardinality") +
  theme(legend.position = "bottom") 
```

### Regression fit

Let us try to fit the results using function $y=c_1 s^{(c_2p)} m^{c_3p}$ (different functions was tried and this gave the highest $R^2$) for each method:

```{r}
# Fit exponential regression model
library(tidymodels)
tidymodels_prefer()
lm_spec <- linear_reg()
# lm_fit <- fit(lm_spec, log(card) ~ -1 + method + method:I(p * log(spAveCard)) + method:I(p * log(m)) + I(log(spAveCard)), data = dat)
# summary(lm_fit)
# tidy(lm_fit)

regressions <- 
  dat %>%
  nest(data = c(-method)) %>% 
  mutate(
    fit = map(data, ~ lm(log(card) ~ I(p * log(spAveCard)) + I(p * log(m)), data = .x)),
    tidied = map(fit, tidy),
    glanced = map(fit, glance)
  )

regressions %>% 
  select(-data) |> 
  unnest(glanced)

# test <- function(p, spAveCard, m) {
#   regressions |> 
#     mutate(p1 = map_dbl(fit, function(x) exp(predict(x, newdata = tibble(spAveCard = spAveCard, m = m, p = p,))))) |> 
#     mutate(p2 = map_dbl(tidied, function(x) exp(x$estimate[1]) * spAveCard^(x$estimate[2] * p) * m^(x$estimate[3] * p)))
#   # cf <- coef |> filter(method == "u") |> select(-method) |> unlist()
#   # return(cf[1] * spAveCard^(cf[2] * p) * m^(cf[3] * p))
# }
# test(p = 3, spAveCard = 200, m = 3)

coef <- regressions %>% 
  select(-data) |> 
  unnest(tidied) |> 
  mutate(estimate = if_else(term == "(Intercept)", exp(estimate), estimate),
         coef = rep(c("c1", "c2", "c3"), 4)) |> 
  select(method, coef, estimate) |> 
  pivot_wider(names_from = coef, values_from = estimate)
coef

# model <- lm(log(card) ~ -1 + method + method:I(p * log(spAveCard)) + method:I(p * log(m)), data = dat)
# summary(model)
# par(mfrow=c(2,2))
# plot(model)
```

The parameters estimates are:

```{r}
model <- lm(log(card) ~ -1 + method + method:I(p * log(spAveCard)) + method:I(p * log(m)), data = dat)
# some plots
library(plotly)
spAveCard <- seq(100, 300, by = 10)
m <- 1:5
p <- 3
method <- factor("l", levels = unique(dat$method))
card <- t(outer(spAveCard, m, function(spAveCard, m) exp(predict(model, newdata = tibble(spAveCard = spAveCard, m = m, p = p, method = method)))))
dat1 <- expand_grid(m = m, p = p, spAveCard = spAveCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- plot_ly() %>%
  add_surface(x = spAveCard, y = m, z = card,
    contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), colorscale = "Viridis", opacity = 0.8)
  # add_trace(type = 'scatter3d',
  #           mode = 'markers',
  #           data = dat1,
  #           x = ~spAveCard, y = ~m, z = ~card,
  #           marker = list(color = 'red', size = 5, symbol = 'circle'))

method <- factor("m", levels = unique(dat$method))
card <- t(outer(spAveCard, m, function(spAveCard, m) exp(predict(model, newdata = tibble(spAveCard = spAveCard, m = m, p = p, method = method)))))
dat1 <- expand_grid(m = m, p = p, spAveCard = spAveCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- fig |> add_surface(x = spAveCard, y = m, z = card,
  contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), colorscale = 'Rainbow', opacity = 1)

method <- factor("ul", levels = unique(dat$method))
card <- t(outer(spAveCard, m, function(spAveCard, m) exp(predict(model, newdata = tibble(spAveCard = spAveCard, m = m, p = p, method = method)))))
dat1 <- expand_grid(m = m, p = p, spAveCard = spAveCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- fig |> add_surface(x = spAveCard, y = m, z = card,
  contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), colorscale = 'heat', opacity = 1)

method <- factor("u", levels = unique(dat$method))
card <- t(outer(spAveCard, m, function(spAveCard, m) exp(predict(model, newdata = tibble(spAveCard = spAveCard, m = m, p = p, method = method)))))
dat1 <- expand_grid(m = m, p = p, spAveCard = spAveCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- fig |> add_surface(x = spAveCard, y = m, z = card,
  contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), colorscale = 'Cividis', opacity = 1) |> 
  layout(
    title = list(
      x = 0.5, y = 0.9, z = 0.9, xanchor = "center",
      text = "Yn for p = 3 and method u, m, ul and l (higest Yn)"  # Title text
    ),
    scene = list(
    xaxis = list(range = range(spAveCard)),  # Set x-axis limits
    yaxis = list(range = range(m),  # Set y-axis limits
    zaxis = list(range = range(card))     # Set z-axis limits
  ))) 

fig
```



```{r}
spAveCard <- seq(100, 300, by = 10)
m <- 1:5
p <- 4
method <- factor("m", levels = unique(dat$method))
card <- t(outer(spAveCard, m, function(spAveCard, m) exp(predict(model, newdata = tibble(spAveCard = spAveCard, m = m, p = p, method = method)))))
dat1 <- expand_grid(m = m, p = p, spAveCard = spAveCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- plot_ly() %>%
  add_surface(x = spAveCard, y = m, z = card,
    contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), opacity = 0.8)

p <- 3
card <- t(outer(spAveCard, m, function(spAveCard, m) exp(predict(model, newdata = tibble(spAveCard = spAveCard, m = m, p = p, method = method)))))
dat1 <- expand_grid(m = m, p = p, spAveCard = spAveCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- fig |> add_surface(x = spAveCard, y = m, z = card,
  contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), opacity = 0.8) 

p <- 2
card <- t(outer(spAveCard, m, function(spAveCard, m) exp(predict(model, newdata = tibble(spAveCard = spAveCard, m = m, p = p, method = method)))))
dat1 <- expand_grid(m = m, p = p, spAveCard = spAveCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig |> add_surface(x = spAveCard, y = m, z = card,
  contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), opacity = 0.8) |> 
  layout(
    title = list(
      x = 0.5, y = 0.9, z = 0.9, xanchor = "center",
      text = "Yn for p = 2-4 and method m"  # Title text
    ),
    scene = list(
    xaxis = list(range = range(spAveCard)),  # Set x-axis limits
    yaxis = list(range = range(m),  # Set y-axis limits
    zaxis = list(range = range(card))     # Set z-axis limits
  ))) 
```




## Relative size of $Y_N$

```{r}
dat %>% 
  ggplot(aes(x = spAveCard, y = card / ubCard, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ m, labeller = "label_both")  + 
  labs(title = "Relative size of nondominated points compared to total enumeration given subproblem cardinality",
       y = "Cardinality Yn",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r, eval=FALSE}
dat %>% 
  ggplot(aes(x = spAveCard, y = card / ubCard, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ m, labeller = "label_both")  + 
  labs(title = "Relative size of nondominated points compared to total enumeration given subproblem cardinality (log2 scale)",
       y = "Cardinality Yn",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") +
  scale_y_continuous(trans = "log2")
```

```{r}
dat %>% 
  ggplot(aes(y = card / ubCard, x = method, color = method)) +
  geom_boxplot() +
  facet_grid(p ~ m, labeller = label_both) +
  labs(title = "Relative size of nondominated points compared to total enumeration",
       y = "%",
       x = "Method",
       color = "Method(s) used to generate subproblems") +
  theme(legend.position = "bottom")
```


```{r, eval=FALSE}
dat %>% 
  ggplot(aes(y = card / ubCard, x = method, color = method)) +
  geom_boxplot() +
  facet_grid(m ~ p, labeller = label_both) +
  labs(title = "Relative size of nondominated points compared to total enumeration (log2 scale)",
       y = "%",
       x = "Method",
       color = "Method(s) used to generate subproblems") +
  theme(legend.position = "bottom") +
  scale_y_continuous(trans = "log2")
```


<!-- ```{r} -->
<!-- dat %>%  -->
<!--   ggplot(aes(y = card / points_hypercube, x = method, color = method)) + -->
<!--   geom_boxplot() + -->
<!--   facet_grid(m ~ p, margins = T, labeller = label_both) + -->
<!--   labs(title = "Relative size of nondominated points compared to total enumeration", -->
<!--        y = "%", -->
<!--        x = "Method", -->
<!--        color = "Method(s) used to generate subproblems") + -->
<!--   theme(legend.position = "bottom") -->
<!-- ``` -->


## Nondominated points classification

We classify the nondominated points into, extreme, supported non-extreme and unsupported.

```{r}
dat %>% 
  ggplot(aes(x = spAveCard, y = pctExt, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ m, margins = T, labeller = label_both)  + 
  labs(title = "Relativ number of extreme points given subproblem cardinality",
       y = "%",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = p, y = pctExt, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(spAveCard ~ m, margins = T, labeller = label_both)  + 
  labs(title = "Relativ number of extreme points given subproblem cardinality",
       y = "%",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = m, y = pctExt, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ spAveCard, margins = T, labeller = label_both)  + 
  labs(title = "Relativ number of extreme points given subproblem cardinality",
       y = "%",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = spAveCard, y = pctSup, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ m, margins = T, labeller = label_both)  + 
  labs(title = "Relativ number of supported points given subproblem cardinality",
       y = "%",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = method, y = pctExt, color = method)) +
  geom_boxplot() + 
  facet_grid(p ~ m, margins = T, labeller = label_both) +
  labs(title = "Relativ number of extreme points given method",
       y = "%",
       x = "Method",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom")
```

```{r}
dat %>% 
  ggplot(aes(x = spAvePctExt, y = pctExt, color = method)) +
  geom_point() + 
  facet_grid(p ~ m, margins = T, labeller = label_both) +
  labs(title = "Relativ number of extreme points",
       y = "% extreme master",
       x = "Avg. % extreme subproblems",
       color = "Method(s) used to generate subproblems") +
  theme(legend.position = "bottom")
```


```{r}
dat %>% 
  ggplot(aes(x = spAvePctExt, y = pctExt, color = factor(spAveCard), shape = method)) +
  geom_point() + 
  facet_grid(p ~ m, margins = T, labeller = label_both) +
  labs(title = "Relativ number of extreme points",
       y = "% extreme master",
       x = "Avg. % extreme subproblems",
       color = "Subproblem cardinality") +
  theme(legend.position = "bottom")
```


```{r}
dat %>% 
  ggplot(aes(y = pctExt/spAvePctExt, x = spAveCard, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ m, margins = T, labeller = label_both) +
  labs(title = "Relativ: % extreme master / % extreme subproblems",
       y = "% extreme master / % extreme subproblems",
       x = "Subproblem cardinality",
       color = "Method(s) used to generate subproblems") +
  theme(legend.position = "bottom")
```

Relative number of extreme:

```{r}
dat |> 
  summarise(minPctEx = min(pctExt, na.rm = T), avePctExt = mean(pctExt, na.rm = T), maxPctEx = max(pctExt, na.rm = T)) 

dat |> 
  group_by(method) |> 
  summarise(minPctEx = min(pctExt, na.rm = T), avePctExt = mean(pctExt, na.rm = T), maxPctEx = max(pctExt, na.rm = T)) |> 
  arrange(desc(avePctExt))
```


## Problems solved for the analysis  

```{r, out.width = "100%"}
DT::datatable(dat, width = "100%", options = list(autoWidth = T, scrollX = TRUE, columnDefs = list(list(width = '250px', targets = c(1)))))
```
